%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

% \usepackage{hyperref}
% \hypersetup{
%     colorlinks=false,
%     % linkcolor=red,
%     filecolor=red,      
%     urlcolor=red,
% }

\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% ... into this one (without comma).
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    .\strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\newcommand*{\cventryalt}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% ... into this one (without comma).
    \ifthenelse{\equal{#5}{}}{}{ #5}%
    \ifthenelse{\equal{#6}{}}{}{ #6}%
    .\strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\newcommand*{\auxentry}[2]{\cventryalt{#1}{}{}{#2}{}{}}
\newcommand*{\cvspace}{\vspace{0.1in}}
% \newcommand*{\me}{\textbf{S. Zhang}}
\newcommand*{\me}{\textbf{Shangtong Zhang}}
\newcommand*{\cvpaper}[5]{\cventryalt{#1}{\textit{\normalfont{#2}}}{}{}{}{#3\leavevmode\newline\textit{#4}{\color{gray}{ #5}}}}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Shangtong} % Your first name
\familyname{Zhang} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{St Catherine's College, Manor Road, Oxford}{United Kingdom, OX1 3UJ}
% \mobile{(000) 111 1111}
% \phone{(000) 111 1112}
% \fax{(000) 111 1113}
\email{shangtong.zhang@cs.ox.ac.uk}
\homepage{shangtongzhang.github.io/}{https://shangtongzhang.github.io/} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-2] % Dummy text
% \lipsum[4] % Dummy text

% \makeletterclosing % Print letter signature

% \newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

% \section{Research Interest}
The goal of my research is to solve sequential decision making problems in an efficient, scalable, and reliable way.
Currently, I focus on off-policy and offline reinforcement learning as a solution method.

\section{Education}
\cventry{2018 - 2022}{Doctor of Philosophy in Computer Science}{University of Oxford}{}{}{}
\auxentry{Advisor}{Prof. Shimon Whiteson}

\cventry{2016 - 2018}{Master of Science in Statistical Machine Learning}{University of Alberta}{}{}{}
\auxentry{Advisor}{Prof. Richard S. Sutton}

\cventry{2012 - 2016}{Bachelor of Science in Computing Science}{Fudan University}{}{}{}
\auxentry{Advisor}{Prof. Wenqiang Zhang and Prof. Xiaoqing Zheng}

\section{Employments}
\cventry{2021.06 - 09}{Research Intern}{Microsoft Research Montreal, Canada}{}{}{}
\cventry{2021.02 - 06}{Research Intern}{DeepMind, London, United Kingdom}{}{}{}
\cventry{2020.09 - 12}{Research Intern}{DeepDrive, Edmonton, Canada}{}{}{}
\cventry{2020.06 - 08}{Research Intern}{Microsoft Research Montreal, Canada}{}{}{}
\cventry{2018.05 - 08}{Research Intern}{Noah's Ark Lab, Huawei, Edmonton, Canada}{}{}{}
\cventry{15.07 - 16.05}{Software Developer Intern}{SAP Labs, Shanghai, China}{}{}{}
\section{Publications (\href{https://scholar.google.co.uk/citations?user=Pn7fj4IAAAAJ&hl=en}{Google Scholar})}

\subsection{Preprints}
\cvpaper{arXiv}{A Deeper Look at Discounting Mismatch in Actor-Critic Algorithms}{\me, Romain Laroche, Harm van Seijen, Shimon Whiteson, \\Remi Tachet des Combes.}{arXiv:2010.01069 (2020).}{}

\subsection{Refereed Articles}
\cvpaper{ICML-21}{Breaking the Deadly Triad with a Target Network}{\me, Hengshuai Yao, Shimon Whiteson.}{International Conference on Machine Learning (2021)}{Acceptance rate: 21.5\%.}
\cvpaper{ICML-21}{Average-Reward Off-Policy Policy Evaluation with Function Approximation}{\me$^*$, Yi Wan$^*$, Richard S. Sutton, Shimon Whiteson.}{International Conference on Machine Learning (2021)}{Acceptance rate: 21.5\%.}
\cvpaper{AAAI-21}{Mean-Variance Policy Iteration for Risk-Averse Reinforcement Learning}{\me, Bo Liu, Shimon Whiteson.}{AAAI Conference on Artificial Intelligence (2021).}{Acceptance rate: 21.4\%.}
\cvpaper{NeurIPS-20}{Learning Retrospective Knowledge with Reverse Reinforcement Learning}{\me, Vivek Veeriah, Shimon Whiteson.}{Conference on Neural Information Processing Systems (2020).}{Acceptance rate: 20.1\%.}
\cvpaper{ICML-20}{GradientDICE: \newline Rethinking Generalized Offline Estimation of Stationary Values}{\me, Bo Liu, Shimon Whiteson.}{International Conference on Machine Learning (2020).}{Acceptance rate: 21.8\%.}
\cvpaper{ICML-20}{Provably Convergent Two-timescale Off-Policy Actor-Critic \newline with Function Approximation}{\me, Bo Liu, Hengshuai Yao, Shimon Whiteson.}{International Conference on Machine Learning (2020).}{Acceptance rate: 21.8\%.}
\cvpaper{AAMAS-20}{Deep Residual Reinforcement Learning}{\me, Wendelin Boehmer, Shimon Whiteson.}{International Conference on Autonomous Agents and Multiagent Systems (2020).}{\newline Acceptance rate: 23\%. {\color{black} \textbf{Best Paper Award}}.}
\cvpaper{AAAI-20}{Mega-Reward: Achieving Human-Level Play without Extrinsic Rewards}{
Yuhang Song, Jianyi Wang, Thomas Lukasiewicz, Zhenghua Xu, \me, Andrzej Wojcicki, Mai Xu}{AAAI Conference on Artificial Intelligence (2020).}{Acceptance rate: 20.6\%.}
\cvpaper{NeurIPS-19}{DAC: The Double Actor-Critic Architecture for Learning Options}{\me, Shimon Whiteson.}{ Conference on Neural Information Processing Systems (2019).}{Acceptance rate: 21.2\%.}
\cvpaper{NeurIPS-19}{Generalized Off-Policy Actor-Critic}{\me, Wendelin Boehmer, Shimon Whiteson.}{Conference on Neural Information Processing Systems (2019).}{Acceptance rate: 21.2\%.}
\cvpaper{ICML-19}{Distributional Reinforcement Learning for Efficient Exploration}{Borislav Mavrin, \me, Hengshuai Yao, Linglong Kong, \\Kaiwen Wu, Yaoliang Yu}{International Conference on Machine Learning (2019)$^\dag$.}{Acceptance rate: 22.6\%. \newline A short version is accepted as an extended abstract at AAMAS 2019.}
\cvpaper{AAAI-19}{ACE: \newline An Actor Ensemble Algorithm for Continuous Control with Tree Search}{\me, Hao Chen, Hengshuai Yao.}{AAAI Conference on Artificial Intelligence (2019).}{Acceptance rate: 16.2\%.}
\cvpaper{AAAI-19}{QUOTA: The Quantile Option Architecture for Reinforcement Learning}{\me, Borislav Mavrin, Linglong. Kong, Bo Liu, Hengshuai Yao.}{AAAI Conference on Artificial Intelligence (2019).}{Acceptance rate: 16.2\%.}
\cvpaper{JOSS-18}{MLPack 3: A Fast, Flexible Machine Learning Library}{Ryan Curtin, Marcus Edel, Mikhail Lozhnikov, Yannis Mentekidis, Sumedh Ghaisas, \\\me}{Journal of Open Source Software (2018).}{}
\cvpaper{ECML-17}{Crossprop: Learning Representations by Stochastic Meta-Gradient Descent \newline in Neural Networks}{Vivek Veeriah$^*$, \me$^*$, Richard S. Sutton.}{European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (2017).}{Acceptance rate: 27.1\%.}
\cvpaper{ICMR-15}{A Deep Neural Network for Modeling Music}{Pengjing Zhang, Xiaoqing Zheng, Wenqiang Zhang, Siyan Li, Sheng Qian, Wenqi He, \me, Ziyuan Wang}{International Conference on Multimedia Retrieval (2015).}{Acceptance rate: 31\%.}
\subsection{Others}
\cvpaper{NIPS-17}{A Deeper Look at Experience Replay}{\me, Richard S. Sutton.}{Deep Reinforcement Learning Symposium.}{}
\cvpaper{NIPS-17}{Comparing Deep Reinforcement Learning and Evolutionary Methods \newline in Continuous Control}{\me, Osmar R. Zaiane}{Deep Reinforcement Learning Symposium.}{}
\cvpaper{NIPS-17}{A Demon Control Architecture with Off-Policy Learning \newline and Flexible Behavior Policy}{\me, Richard S. Sutton.}{Hierarchical RL Workshop.}{}

$^*$: {\color{gray}Equal contribution} \\
$^\dag:$ {\color{gray} My name does not appear in the ICML camera-ready copy due to a mistake in submission, see Acknowledgments, arXiv, or AAMAS proceedings for clarification.}
\section{Open-Source Code}
\cventry{}{\href{https://github.com/ShangtongZhang/DeepRL}{PyTorch Deep RL}}{}{}{}{A zoo of popular deep RL algorithms in PyTorch with \textbf{2.4k stars} in Github.}
% \cvspace
\cventry{}{\href{https://github.com/ShangtongZhang/reinforcement-learning-an-introduction}{Reinforcement Learning: An Introduction}}{}{}{}{Python implementation of the RL book \textit{Reinforcement Learning: An Introduction} \\ with \textbf{10.1k stars} in Github.}
% \cvspace
\cventry{}{\href{https://summerofcode.withgoogle.com/archive/2017/projects/4800276775043072/}{Google Summer of Code (GSoC) 2017}}{}{}{}{Contributed to MLPack by implementing a deep RL framework.}
% \cvspace
\cventry{}{\href{https://www.google-melange.com/archive/gsoc/2014/orgs/xapian/projects/shangtongzhang.html}{Google Summer of Code (GSoC) 2014}}{}{}{}{Contributed to Xapian by optimizing the post list and the position list.}


\section{Academic Services}
\cventry{}{Expert Reviewer}{}{}{}{ICML 2021}
\cventry{}{Reviewer \& Program Committee Member}{}{}{}{NeurIPS 2020, 2021, ICML 2020, AAAI 2020, 2021, ICLR 2021, 2022 \\
Offline Reinforcement Learning Workshop at NeurIPS 2020 \\
Deep Reinforcement Learning Workshop at NeurIPS 2019, 2020, 2021 \\
Adaptive and Learning Agents Workshop at AAMAS 2019, 2020 \\
Optimization Foundations for Reinforcement Learning Workshop at NeurIPS 2019 \\
Reinforcement Learning for Real Life Workshop at ICML 2019, 2021\\
% IEEE Transactions on Cybernetics 2019
}
\section{Awards \& Honours}
\cventry{2018 - 2022}{EPSRC studentship}{University of Oxford}{}{}{}
\cventry{2021}{ICLR Outstanding Reviewer}{}{}{}{}
\cventry{2020}{NeurIPS Reviewer Award (Top 10\%)}{}{}{}{}
\cventry{2020}{ICML Reviewer Award (Top 33\%)}{}{}{}{}
\cventry{2020}{Light Senior Scholarship}{St Catherine's College, University of Oxford}{}{}{}
\cventry{2020}{AAMAS Travel Award}{}{}{}{}
\cventry{2020}{AAMAS Best Paper Award}{}{}{}{}
\cventry{2019}{NeurIPS Optimization Foundations for RL Workshop Travel Award}{}{}{}{}
\cventry{2019}{NeurIPS Travel Award}{}{}{}{}
\cventry{2019}{AAAI Travel Award}{}{}{}{}
\cventry{2017}{NIPS Hierarchical RL Workshop Travel Award}{}{}{}{}
\cventry{2015}{Second Class Scholarship}{Fudan University}{}{}{}
\cventry{2014}{EMC Scholarship}{Fudan University}{}{}{}

\section{Invited Talks}
\cventry{2020}{Off-Policy Evaluation}{}{}{Data Fest 2020, Open Data Science}{}
\cventry{2020}{Off-Policy Evaluation and Control}{}{}{ByteDance AI Lab, Shanghai}{}
\cventry{2019}{Off-Policy Actor-Critic Algorithms}{}{}{Latent Logic LTD, Oxford}{}
\cventry{2019}{Generalized Off-Policy Actor-Critic}{}{Noah's Ark Lab, Huawei, Edmonton}{}{}
\cventry{2018}{Exploration with Quantile Options}{}{Huawei RL Workshop, Edmonton}{}{}
\cventry{2017}{Coding Deep Reinforcement Learning Papers}{}{}{}{NIPS MLTrain Workshop, Long Beach.}
\section{Teaching}
\cventry{Michaelmas 2019}{Teaching Assistant}{University of Oxford}{}{}{AIMS CDT Lectures}
\cventry{Fall 2016}{Teaching Assistant}{University of Alberta}{}{}{CMPUT 229 Computer Organization and Architecture}


% \section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

% \cvlistdoubleitem{Piano}{Chess}
% \cvlistdoubleitem{Cooking}{Dancing}
% \cvlistitem{Running}

%----------------------------------------------------------------------------------------

\end{document}